Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet in IC~2602

### 2020-05-11 paper/ms.tex
update paper

\begin{abstract}
We report the discovery of the transiting planet TOI 837.01,
a warm Jupiter-sized planet ($R_{\rm p} = 10.XX\,R_\oplus$, $P =
8.YY\,{\rm d}$), with mass less than X.XX $M_{\rm Jup}$.
TOI$\,$837.01 orbits a V=10.6, T=9.9 G-dwarf in IC~2602, also known as the
``Southern Pleiades'', and is therefore 50 million years old.
We characterize the system using data from the NASA {\it Transiting
Exoplanet Survey Satellite} (TESS), the ESA Gaia mission,
ground-based photometry, and spectroscopy from CTIO1.5/CHIRON,
XXX/FEROS, and AAT/Veloce.
TOI 837.01 joins the growing ranks of adolescent exoplanets orbiting
bright host stars, and is amenable for studies of planetary
atmospheric and orbital evolution.
\end{abstract}

@@

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black),
  and stars in the neighborhood (gray).} Members (black circles) were
  identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
  delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
  direction, and ${\rm RV}$ radial velocity reported by Gaia-DR2.  The
  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
  proper motion projection ($\mu_{\rm delta}$ vs{.} $\mu_{\rm
  \alpha}\cos\delta$) highlights the incomplete membership selection
  function.
  \label{fig:full_kinematics}
	}
\end{figure*}

>>>>

\begin{abstract}
We report the discovery of the transiting planet TOI 837.01,
a warm Jupiter-sized planet ($R_{\rm p} = 10.XX\,R_\oplus$, $P =
8.YY\,{\rm d}$), with mass less than X.XX $M_{\rm Jup}$.
TOI$\,$837.01 orbits a V=10.6, T=9.9 G-dwarf in IC~2602 (the
``Southern Pleiades'') and is therefore 50 million years old.
We characterize the system using data from the NASA {\it Transiting
Exoplanet Survey Satellite} (TESS), the ESA Gaia mission,
ground-based photometry, and spectroscopy from CTIO1.5/CHIRON,
XXX/FEROS, and AAT/Veloce.
TOI 837.01 joins the growing ranks of adolescent exoplanets orbiting
bright host stars, and is amenable for studies of planetary
atmospheric and orbital evolution.
\end{abstract}

@@

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Positions and kinematics of \tn\ (star), \cn\ members (black
  circles), and stars in the neighborhood (gray circles).} Members
  were identified by \citet{cantatgaudin_gaia_2018}.  $\alpha$ denotes
  right ascension, $\delta$ declination, $\pi$ parallax, $\mu_{\rm
  delta}$ and $\mu_{\rm \alpha}$ proper motion in each equatorial
  direction, and ${\rm RV}$ radial velocity reported by Gaia-DR2.  The
  RVs are for unblended spectra of bright stars ($G\lesssim 12$).  The
  proper motion projection ($\mu_{\delta}$ vs{.} $\mu_{\rm
  \alpha}\cos\delta$) highlights the membership selection function.
  \label{fig:full_kinematics}
	}
\end{figure*}
